Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex
minor edits

\begin{example}
\label{ex:base-377}
Here we demonstrate, in detail, that case (b) ($\sigma_2 =
(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
We have that $\halfcan' \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
We exhibit a (minimal) presentation for $R'$.

@@

\begin{longtable}
	{| c | c | c || c | c |}
	\hline
	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$\\
	\hline
	\hline

	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & 1 & 0\\	\hline

	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & 1 & 0\\ \hline

	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & 2 & 0\\ \hline

	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & 1 & 0\\ \hline

	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & 2 & 0\\ \hline

	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & 3 & 0\\ \hline

	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & 2 & 0\\ \hline

	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & 3 & 0\\ \hline

	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & 4 & 0\\ \hline

	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & 5 & 0\\ \hline

	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0\\ \hline
\end{longtable}

>>>>

\begin{example}
\label{ex:base-377}
Here we demonstrate, in detail, that case (b) with ($\sigma_2 =
(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
We have that $\halfcan' \sim -(\infty) + \frac{1}{3} P_1 +
\frac{3}{7} P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
We exhibit a (minimal) presentation for $R'$.

@@

\begin{longtable}
	{| c | c | c || c | c |}
	\hline
	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
	\hline
	\hline

	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & 1 & 0 \\	\hline

	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & 1 & 0 \\ \hline

	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & 2 & 0 \\ \hline

	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & 1 & 0 \\ \hline

	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & 2 & 0 \\ \hline

	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & 3 & 0 \\ \hline

	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & 2 & 0 \\ \hline

	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & 3 & 0 \\ \hline

	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & 4 & 0 \\ \hline

	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & 5 & 0 \\ \hline

	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0 \\ \hline
\end{longtable}
